deaths_explanation

### 2024-04-24 deaths_explanation.qmd
Added more notes

@@

JG - This little table on the right shows the CHD deaths (same data that forms the numerator of my project calculation) as a crude rate per 10,000 population, as well as all cause deaths as  crude rate. The table on the left is mortality rates age and sex standardised using census population. So, if the age and sex standardised mortality rates show the most diverse cluster to have the highest rate then why do the project rates using need not follow the same pattern?

@@

>>>>

SW - Are they dying of other causes? = No

@@

JG - The table on the right shows the CHD deaths (same data that forms the numerator of the project calculation) as a crude rate per 10,000 population, as well as all cause deaths as crude rate. The table on the left is mortality rates age and sex standardised using census population. So, if the age and sex standardised mortality rates show the most diverse cluster to have the highest rate then why do the project rates using need not follow the same pattern?

@@

SC - higher incidence and better survival?

On register:

![](secret/cvdreg.png){fig-align="center"}

Deaths:

![](secret/deaths.png){fig-align="center"}
